Diversity dynamics in Nymphalidae butterflies: Effect of phylogenetic uncertainty on diversification rate shift estimates

### 2015-01-14 response_to_reviewers.tex

\textbf{34. Response:}
\begin{quote}
\color{blue}
We revised the paragraph according to the reviewer's suggestion.
\end{quote}

\textbf{35. Reviewer's Comment:}
Page 10, Figure legends, figure 1: Include a description of what nodes 1 and
19 are as well.

\textbf{35. Response:}
\begin{quote}
\color{blue}
We added the description of nodes 1 and 19 to the legend as suggested by the
reviewer.
\end{quote}

\textbf{36. Reviewer's Comment:}
Page 10, Figure legends, figure 2: are these rates estimated in MEDUSA or MultiMEDUSA analyses?

\textbf{36. Response:}
\begin{quote}
\color{blue}
We corrected the legend as the rates were estimated by MultiMEDUSA and not by
MEDUSA.
\end{quote}

\textbf{37. Reviewer's Comment:}
Page 11, Figure legends, figure 4: the legend is missing a closing parenthesis,
“)”.
\textbf{37. Response:}
\begin{quote}
\color{blue}
We added the required closing parenthesis.
\end{quote}

### 2015-01-14 MS_revised.tex
comment 36
comment 37

{\bf Figure 2. Diversification rates for taxa estimated by MEDUSA on
the samples of 1000 random trees}

@@

{\bf Figure 4. BiSSE analysis of diversification of nymphalids due
to feeding on Solanaceae hostplants} Speciation and net diversification
rates are significantly higher in Solanaceae feeders (speciation rate =
$\lambda1$, net diversification rate = $r1$.

>>>>

{\bf Figure 2. Diversification rates for taxa estimated by MultiMEDUSA on
the samples of 1000 random trees}

@@

{\bf Figure 4. BiSSE analysis of diversification of nymphalids due
to feeding on Solanaceae hostplants} Speciation and net diversification
rates are significantly higher in Solanaceae feeders (speciation rate =
$\lambda1$, net diversification rate = $r1$).
